
% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2015}

\begin{thebibliography}
\textbf{[1]} Defending From Within: How Insiders Threaten Data Privacy‖ report by Informatics and Government Business Council. https://www.informatica.com/ content/dam/inform atica- com/global/amer/us/ collateral/executive- brief/defending-from-withingbc\_executive-brief\_2591.pdf.\\\\


\textbf{[2]} William Stallings‖ Cryptography and Network
Security: Principles and Practice‖ Prentice Hall; 5
edition (14 Jan. 2010).\\\\


\textbf{[3]} Mohammed J. Novel Approaches to Big Data
Management. ISSN 2348-1196 (print) International
Journal of Computer Science and Information
Technology Research ISSN 2348-120X (online)
Vol. 3, Issue 1, pp: (96- 105), Month: January - March
2015.\\\\

\textbf{[4]} Mohammed J. The State of Cryptography- A National
Interest Perspective. ISO 9001:2008Certified
International Journal of Engineering and Innovative
Technology (IJEIT) Volume 4, Issue 8, February
2015.\\\\

\textbf{[5]} Imperva White Paper ―Top Ten Database Threats‖
2014. http://www.imperva.com/
docs/WP\_TopTen\_Data base\_Threats.pdf.
International Journal of Computer Science & Emerging
Technologies (E-ISSN: 2044-6004) 368 Volume 2,
Issue 3, June 2011, page(s); 368- 372.\\\\


\textbf{[6]} Tanya Bacca; Making Database Security an IT Security
Priority A SANS Whitepaper – November 2009.\\\\


\textbf{[7]} 2012 future of cloud computing survey results – North
Bridge http://northbridge.com/2012-cloud-computingsurvey.\\\\

\textbf{[8]} Iqra Basharat, Farooque Azam, Abdul Wahab
Muzaffar,‖Database Security and Encryption: A Survey
Study‖, International Journal of Computer
Applications (0975 – 888) Volume 47– No.12,
June 2012.\\\\


\textbf{[9]} Mr. Saurabh Kulkarni, Dr. Siddhaling Urolagin,
―Review of Attacks on Databases and Database
Security Techniques‖, International Journal of
Emerging Technology and Advanced Engineering,
ISSN 2250-2459, Volume 2, Issue 11,
November 2012.\\\\

\textbf{[10]}Networking and Security- Tech Soup for Libraries
https://www.techsoupforlibraries.org/book/export
/html/592\\\\

\textbf{[11]} Amichai Shulman; Top Ten Database Security Threats,
How to Mitigate the Most Significant Database
Vulnerabilities, 2006 White Paper.\\\\

\textbf{[12]} Mohammed J. (2015). The state of cryptography- a
national interest perspective. International journal of
engineering and innovative technology, 181-
192.\\\\

\textbf{[13]} Information Security
http://en.wikipedia.org/wiki/information \_security.\\\\
\textbf{[14]} Mohammed, J. (2014). Web and cloud security.
International journal of engineering technology and
advanced engineering. \\\\

\textbf{[15]} Kadhem, H.; Amagasa, T.; Kitagawa, H.; A Novel
Framework for Database Security based on Mixed
Cryptography; Internet and Web Applications and
Services, 2009. ICIW '09. Fourth International
Conference on; Publication Year:
2009, Page(s): 163 – 170.\\\\
\textbf{[16]} Iqra Basharat , Farooque Azam , Abdul Wahab
Muzaffar ―Database Security and Encryption: A
Survey Study‖.\\\\

\\\\\\\\\\\\\\\\\\\\\\\\

\end{thebibliography}
